A Simple Ratio for Estimating the Effective Reproduction Value of an Epidemic

### 2021-01-16 docs/manuscript/manuscript.Rmd
Made derivation of simple-ratio more descriptive

```{=tex}
\begin{equation} 
  I_t = \int_a^\infty{I_{t-a}n(a)}da
  (\#eq:renewal-eq)
\end{equation}
```
The generation interval distribution is equal to $n(a)$ normalized by the total number of infections a single infected person is expected cause (i.e. $R_t$).

```{=tex}
\begin{equation} 
  g(a) = \frac{n(a)}{R_t}
  (\#eq:generation-interval-eq)
\end{equation}
```
Thus, Equation \@ref(eq:generation-interval-eq) can be substituted into Equation \@ref(eq:renewal-eq) to produce:

```{=tex}
\begin{equation} 
  \frac{I_t} = \int_a^\infty{I_{t-a}\frac{g(a)}{R_t}}da
  (\#eq:sub-in-rt-1)
\end{equation}
```
```{=tex}
\begin{equation} 
  \frac{I_t}{R_t} = \int_a^\infty{I_{t-a}g(a)}da
  (\#eq:sub-in-rt-2)
\end{equation}
```
```{=tex}
\begin{equation} 
  R_t = \frac{I_t}{\int{I_{t-a}g(a)}da}
  (\#eq:sub-in-rt-3)
\end{equation}
```
If we make the assumption that there is minimal variance in the generation interval distribution (i.e. $g(a)$ equals approximately 1 when $a$ equals the mean generation interval ($d$) and $g(a)$ equals approximately zero for all other values of $a$), then equation (4) can be simplified to:

>>>>

```{=tex}
\begin{equation} 
  I_t = \int_a^\infty{I_{t-a}n(a)}da
  (\#eq:renewal-eq)
\end{equation}
```
Next we can substitute the generation interval function ($g(a)$) into Equation \@ref(eq:renewal-eq) by recognizing that the generation interval distribution is equal to $n(a)$ normalized by the total number of infections a single infected person is expected cause (i.e. $R_t$).

```{=tex}
\begin{equation} 
  g(a) = \frac{n(a)}{R_t}
  (\#eq:generation-interval-eq)
\end{equation}
```
```{=tex}
\begin{equation} 
  I_t = \int_a^\infty{I_{t-a}\frac{g(a)}{R_t}}da
  (\#eq:sub-in-rt-1)
\end{equation}
```
```{=tex}
\begin{equation} 
  \frac{I_t}{R_t} = \int_a^\infty{I_{t-a}g(a)}da
  (\#eq:sub-in-rt-2)
\end{equation}
```
```{=tex}
\begin{equation} 
  R_t = \frac{I_t}{\int{I_{t-a}g(a)}da}
  (\#eq:sub-in-rt-3)
\end{equation}
```
If we make the assumption that there is minimal variance in the generation interval distribution (i.e. $g(a)$ equals approximately 1 when $a$ equals the mean generation interval ($d$) and $g(a)$ equals approximately zero for all other values of $a$), then Equation \@ref(eq:renewal-eq) can be simplified to:
